---
title: "p8105_hw3_xl2851"
output: github_document
---
# problem 1
## 1.1 How many aisles are there, and which aisles are the most items ordered from?
```{r}
library(p8105.datasets)
library(tidyr)
library(tidyverse)
data("instacart")

```

```{r}
aisle_count=
instacart %>%
  group_by(aisle) %>%
  summarize(number_of_items=n())%>%
  arrange(desc(number_of_items))
```

There are 134 aisles. Fresh vegetables are the most items ordered from.

## 1.2 Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered.
```{r}
plot_aisle =
  aisle_count %>%
  filter(number_of_items>10000)%>%
  ggplot(aes(x=aisle, y=number_of_items))

plot_aisle+geom_point()
```

## 1.3 Make a table showing the three most popular items in each of the aisles
```{r}
pop_item=
  instacart %>%
  filter(aisle == c("baking ingredients","dog food care","packaged vegetables fruits"))%>%
  group_by(aisle,product_name)%>%
  count()%>%
  summarize(
    order_max=max(n))
```

## 1.4 Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week
```{r}
mean_hour=
  instacart %>%
  filter(product_name==c("Pink Lady Apples","Coffee Ice Cream"))%>%
  group_by(order_dow)%>%
  summarize(
    mean=mean(order_hour_of_day)
  )
```

